---
title: "R Notebook"
output: html_notebook
---

File is from: https://colab.research.google.com/drive/1Ws9ZyVpsis825FOVX5fjvTE7N7nV-ZmG#scrollTo=15hz0ZF3hb0b
This is translated from Python to R 

```{r}
# Set the path to the file
file_path <- "~/Desktop/quant_uxr/datasets/BBB.csv"

# Load the .csv file
df <- read.csv(file_path)

# Print the first few rows of the dataset
head(df)

```
Q1: What percentage of customers are female? 

```{r}
# Tabulate the counts for "gender"
gender_counts <- table(df$gender)

# Print the counts
print(gender_counts)

# Calculate the frequencies (proportions)
gender_freq <- prop.table(gender_counts)

# Print the frequencies
print(gender_freq)

```
Q2: What three states account for the largest share of BookBinder's customers? 

```{r}
# Tabulate the counts for "state"
state_counts <- table(df$state)

# Sort the counts in descending order to get the most frequent states first
sorted_counts <- sort(state_counts, decreasing = TRUE)

# Print the sorted counts (Top 3)
print(head(sorted_counts, 3))

#ANSWER = NY, NJ, PA

```

Q3: What is the average Total $ spent, the average Total # of book purchases, and the average number of months since last purchase?

```{r}
total_sum <- sum(df$total_)
print(total_sum)

purch_mean <- mean(df$purch)
print(purch_mean)

last_mean <- mean(df$last)
print(last_mean)

```

Q4: Calculate the correlation between customers’ total spending on books and their total
spending on non-book products. Is the correlation statistically significant?

We will use mba263 pwcorr function, which returns correlation coefficient and p-value for the $\chi^2$ test.
H0 is that correlation coefficient is 0.

```{r}

#we want the correlation between
#1) customers' total spending on books (total_)
#2) their total spending on non-book products (nonbook_)

#pearson correlation - 2 continous variables
    
correlation = cor(df$total_, df$nonbook_, method = "pearson")
print(correlation)

#ANSWER = 0.92, strong positive correlation

```

```{r}

#is this correlation statistically signficant?
    
# Perform correlation test
cor_test <- cor.test(df$total_, df$nonbook_)

# Print results
print(cor_test)

#ANSWER = p-value is less than 0.05, so we reject that there is no correlation (h0) - or in other words, conclude there is correlation between book and non-book spending in the population.

```

Q5: Use a regression as another way to determine whether customers’ total spending on books
and their total spending on non-book products is correlated. Is the coefficient significant?

```{r}

#is this correlation statistically signficant?
#let's answer this with regression instead of pearson's correlation
    
#Fit linear regression model 
model <- lm(df$total_ ~ df$nonbook_)

#Print summary of model
summary(model)

#ANSWER = from this we can see that one dollar increase in non-book spending correlates to one 1.06 dollar increase in total spending. In addition, we can see that this is statistically significant (p-value <0.05). So there's clearly a positive correlation between the value variables and holds at the population at large.

```

Q6: Which book categories have sold the most books? Which have sold the least?

```{r}

df_book_categories = data.frame(df$child,df$youth,df$cook,df$do_it,df$refernce,df$art,df$geog)
head(df_book_categories)

# Calculate sum of each column
column_sums <- colSums(df_book_categories)

# Rank the column sums in descending order
ranked_sums <- sort(column_sums, decreasing = TRUE)

# Print the ranked sums
print(ranked_sums)

# ANSWER = cook is most, reference is least

```

Q7: Create a bar chart showing the average total spending on books for males and females.

```{r}

#install.packages("ggplot2", dependencies = TRUE, reinstall = TRUE)
library(ggplot2)

# Split the data by gender and then sum the total_ for each gender
gender_means <- sapply(split(df$total_, df$gender), mean)

# Tabulate the counts for "gender"
print(gender_means)

# Create a data frame for ggplot
df_sums <- data.frame(gender = names(gender_means), total_sum = gender_means)

# Create the bar plot
ggplot(df_sums, aes(x = gender, y = total_sum, fill = gender)) +
  geom_bar(stat = "identity") +
  labs(title = "Average Total Spending by Gender", x = "Gender", y = "Total Spending") +
  theme_minimal()

```
Q8: Is the average total spending on books statistically different for males and females? 

```{r}

#t-test = 1 categorial (f vs. m) and 1 continuous (total spending) 

#first, we need to recode gender to female (0, 1)
df$gender_recoded <- ifelse(df$gender == "M", 0, 1)

# Run the t-test
t_test_result <- t.test(total_ ~ gender_recoded, data = df)
print(t_test_result)

#ANSWER = yep, it's statistically significant

```
Q9: Answer question 8 using a dummy variable regression. Hint: First transform the gender

```{r}

#is this correlation statistically signficant?
#let's answer this with regression instead of pearson's correlation
    
#Fit linear regression model 
model_gender <- lm(df$total_ ~ df$gender_recoded)

#Print summary of model
summary(model_gender)

#ANSWER = from this we can see that one dollar increase in non-book spending correlates to one 1.06 dollar increase in total spending. In addition, we can see that this is statistically significant (p-value <0.05). So there's clearly a positive correlation between the value variables and holds at the population at large.

```

