---
title: "R Notebook"
output: html_notebook
---

File is from: https://colab.research.google.com/drive/1Ws9ZyVpsis825FOVX5fjvTE7N7nV-ZmG#scrollTo=15hz0ZF3hb0b
This is translated from Python to R 

```{r}
# Set the path to the file
file_path <- "~/Desktop/quant_uxr/datasets/BBB.csv"

# Load the .csv file
df <- read.csv(file_path)

# Print the first few rows of the dataset
head(df)

```
Q1: What percentage of customers are female? 

```{r}
# Tabulate the counts for "gender"
gender_counts <- table(df$gender)

# Print the counts
print(gender_counts)

# Calculate the frequencies (proportions)
gender_freq <- prop.table(gender_counts)

# Print the frequencies
print(gender_freq)

```
Q2: What three states account for the largest share of BookBinder's customers? 

```{r}
# Tabulate the counts for "state"
state_counts <- table(df$state)

# Sort the counts in descending order to get the most frequent states first
sorted_counts <- sort(state_counts, decreasing = TRUE)

# Print the sorted counts (Top 3)
print(head(sorted_counts, 3))

#ANSWER = NY, NJ, PA

```

Q3: What is the average Total $ spent, the average Total # of book purchases, and the average number of months since last purchase?

```{r}
total_sum <- sum(df$total_)
print(total_sum)

purch_mean <- mean(df$purch)
print(purch_mean)

last_mean <- mean(df$last)
print(last_mean)

```

Q4: Calculate the correlation between customers’ total spending on books and their total
spending on non-book products. Is the correlation statistically significant?

We will use mba263 pwcorr function, which returns correlation coefficient and p-value for the $\chi^2$ test.
H0 is that correlation coefficient is 0.

```{r}

#we want the correlation between
#1) customers' total spending on books (total_)
#2) their total spending on non-book products (nonbook_)

#pearson correlation - 2 continous variables
    
correlation = cor(df$total_, df$nonbook_, method = "pearson")
print(correlation)

#ANSWER = 0.92, strong positive correlation

```

```{r}

#is this correlation statistically signficant?
    
# Perform correlation test
cor_test <- cor.test(df$total_, df$nonbook_)

# Print results
print(cor_test)

#ANSWER = p-value is less than 0.05, so we reject that there is no correlation (h0) - or in other words, conclude there is correlation between book and non-book spending in the population.

```

Q5: Use a regression as another way to determine whether customers’ total spending on books
and their total spending on non-book products is correlated. Is the coefficient significant?
